Capstone Movielens Report

### 2025-02-03 reports/capstone-movielens-report.Rmd
Backref support in biblatex

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
output:
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true

  html_document: 
    fig_caption: true
hyperrefoptions:
  - backref
colorlinks: true
linkcolor: red
citecolor: blue
header-includes:
    - \usepackage{hyperref}
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::knitr}
---

```{r setup, include=TRUE, echo = FALSE}
library(RefManageR)
bib <- ReadBib("references.bib", check = FALSE)
BibOptions(check.entries = FALSE,
           hyperlink = "to.bib",
           bib.style = "numeric", 
           style = "markdown", 
           cite.style = 'numeric')

citeB <- function(citeKey){
  Cite(bib, citeKey, .opts = list(super = FALSE))
}

@@

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the _Netflix Grand Prize Contest_ \cite{NYT1MNP} `r #\cite{knuthwebsite}` `r #citeB("NYT1MNP")`  requirements, we will evaluate the RMSE score defined as`r citeB("IDS2_23-2")`:

@@

This is a great conclusion, isn't is?!!

\addcontentsline{toc}{section}{Whole References}
\bibliography{references}
\bibliographystyle{mla-good}

```{r results = "asis", echo = FALSE}
# \addcontentsline{toc}{section}{References}
# \printbibliography[title={Whole bibliography}]
# 
# \color{black}
# \bibliography{references}
#\bibliographystyle{mla-good}
#\bibliographystyle{is-unsrt}
#\bibliographystyle{is-plain}
#\bibliographystyle{is-abbrv}
#\bibliographystyle{apalike}

# PrintBibliography(bib,
#                   .opts = list(check.entries = FALSE,
#                                hyperlink = "to.bib",
#                                first.inits = FALSE,
#                                bib.style = "numeric",
#                                style = "markdown",
#                                cite.style = 'numeric'))

>>>>

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
bibliography: references.bib
#csl: bit-numerical-mathematics.csl 
output:
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
    citation_package: biblatex
  html_document: 
    fig_caption: true
# hyperrefoptions:
#   - backref
colorlinks: true
linkcolor: red
citecolor: blue
header-includes:
    - \usepackage{hyperref}
    - \usepackage[natbib=true, 
                  style=numeric, 
                  backref=true, 
                  sorting=none]{biblatex}
    - \hypersetup{backref,
          pdfpagemode=FullScreen,
          colorlinks=true,
          implicit=false}
    #- \hyper@nopatch@bib = null
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::knitr}
---

```{r setup, include=TRUE, echo = FALSE}
library(RefManageR)
bib <- ReadBib("references.bib", check = FALSE)

BibOptions(check.entries = FALSE,
           hyperlink = "to.bib",
           bib.style = "numeric", 
           style = "markdown", 
           cite.style = 'numeric')

bibFound <- SearchBib(bib)

citeB <- function(citeKey){
  Cite(bibFound[citeKey], .opts = list(super = FALSE))
}

@@

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the _Netflix Grand Prize Contest_[@NYT1MNP] requirements, we will evaluate the RMSE score defined as[@IDS2_23-2]:

@@

This is a great conclusion, isn't it?!!
